Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-08-10 texor.Rmd
Minor Edits to the paper

```{r workflow, fig.cap="Workflow of the document conversion conducted by texor.", out.width="70%", fig.align='center'}
knitr::include_graphics("workflow.png")
```

@@

The HTML output renders math using MathJax. This does mean that some functionality, like `\bm`, `\boldmath` and `mathbb` not supported, and special definitions cannot be handled.

@@

1. The stream editor modifies the `\multicolumnx{..}` to
    `\multicolumnxx{..}`.

2. A LaTeX macro is used to redefine the `\multicolumnxx{..}` to
    `\multicolumnx{---}`.

@@

>>>>

```{r workflow, fig.cap="Workflow of the document conversion conducted by texor.", out.width="90%", fig.align='center'}
knitr::include_graphics("workflow.png")
```

@@

The HTML output renders math using MathJax. This does mean that some functionality, like `\bm`, `\boldmath` and `\mathbbm` not supported, and special definitions can be handled albeit in a limited capacity.

@@

1. The stream editor modifies the `\multicolumn{..}` to
    `\multicolumnx{..}`.

2. A LaTeX macro is used to redefine the `\multicolumnxx{..}` to
    `\multicolumn{---}` (which is accepted by pandoc).

@@

XXX - Should we include various options/params for the function here ?

### 2023-08-10 texor.tex
Minor Edits to the paper

{\centering \includegraphics[width=0.7\linewidth]{workflow}

@@

The HTML output renders math using MathJax. This does mean that some functionality, like \texttt{\textbackslash{}bm}, \texttt{\textbackslash{}boldmath} and \texttt{mathbb} not supported, and special definitions cannot be handled.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  The stream editor modifies the \texttt{\textbackslash{}multicolumnx\{..\}} to
  \texttt{\textbackslash{}multicolumnxx\{..\}}.
\item
  A LaTeX macro is used to redefine the \texttt{\textbackslash{}multicolumnxx\{..\}} to
  \texttt{\textbackslash{}multicolumnx\{-\/-\/-\}}.
\item
  Pandoc reads the table and transforms it to markdown.
\end{enumerate}

>>>>

{\centering \includegraphics[width=0.9\linewidth]{workflow}

@@

The HTML output renders math using MathJax. This does mean that some functionality, like \texttt{\textbackslash{}bm}, \texttt{\textbackslash{}boldmath} and \texttt{\textbackslash{}mathbbm} not supported, and special definitions can be handled albeit in a limited capacity.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  The stream editor modifies the \texttt{\textbackslash{}multicolumn\{..\}} to
  \texttt{\textbackslash{}multicolumnx\{..\}}.
\item
  A LaTeX macro is used to redefine the \texttt{\textbackslash{}multicolumnxx\{..\}} to
  \texttt{\textbackslash{}multicolumn\{-\/-\/-\}} (which is accepted by pandoc).
\item
  Pandoc reads the table and transforms it to markdown.
\end{enumerate}
